---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# B2package

<!-- badges: start -->
<!-- badges: end -->

## Overview

This package was created for Assignment B2 as part of STAT545B in the fall of 2021.

The goal of B2package is to provide a package that contains a function that helps provide a snapshot of one's data. Specifically, this package provides a data snapshot of two numeric variables. It contains a function which returns summary statistics for the numeric variables, as well as a scatterplot and the adjusted R squared value to provide a sense of the linear relationship between the variables (if any). Generally, the adjusted r squared value, a value between 0 and 1, represents the proportion of variance observed for a dependent variable explained by the independent variable in a linear regression model.

## Installation

B2package is not yet on CRAN. But, you can download it from this repository using
the following R command:

``` r
devtools::install_github("hansudd/AssnB2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hansudd/AssnB2", ref = "0.1.0")
```
## Example

This is a basic example which shows you how to quickly visualize and assess the relationship between two numeric variables:

```{r example}
library(B2package)
## basic example code
data_snapshot(mtcars, hp, mpg)
```

This package is helpful if you frequently work on datasets with two numeric variables, and you want to quickly determine if 
there is a linear relationship between the variables. 
