---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# B2package

<!-- badges: start -->
<!-- badges: end -->

## Overview

This package was created for Assignment B2 as part of STAT545B in the fall of 2021.

The goal of B2package is to provide a package that contains a function that helps provide a snapshot of one's data. Specifically, this package provides a data snapshot of two numeric variables. It contains a function which returns summary statistics for the numeric variables, as well as a scatterplot and the adjusted R squared value to provide a sense of the linear relationship between the variables (if any). Generally, the adjusted r squared value, a value between 0 and 1 (displayed as a percentage), represents the proportion of variance observed for a dependent variable explained by the independent variable in a linear regression model.

## Installation

B2package is not yet on CRAN. But, you can download it from this repository using
the following R command:

``` r
devtools::install_github("hansudd/AssnB2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hansudd/AssnB2", ref = "0.1.0")
```
## Examples


__Example 1__ This is an example that shows you how to quickly visualize and assess the relationship between two numeric variables:
```{r example}
# loading the B2package package
library(B2package)

## example 1 of the data_snapshot function 
data_snapshot(mtcars, hp, mpg)



```

Example 1 shows the linear relationship between two numeric variables from the `mtcars` dataset, hp vs mpg. We observe an adjusted r-squared value of 58.92 %. Example 2 will feature an example where there is a stronger linear relationship between the two variables.

__Example 2__ This is another example that shows you how to quickly visualize and assess the relationship between two numeric variables:
```{r}
# example 2 of the data_snapshot function
data_snapshot(mtcars, mpg, wt)
```

Example 2 shows the linear relationship between the variables mpg and wt from the `mtcars` dataset. Here, we report a higher adjusted r-squared value of %.

Hence, from these two usage examples, we see that the `data_snapshot` function returns a scatterplot and the adjusted r squared value when fed two numeric variables.

This package is helpful if you frequently work on datasets with two numeric variables, and you want to quickly determine if 
there is a linear relationship between the variables. 
