---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# B2package

<!-- badges: start -->
<!-- badges: end -->

## Overview

The `B2package` allows users, via the `data_snapshot()` function, to quickly assess summary statistics for and the relationship between two numeric variables from a given dataset.

The `B2package` was created for Assignment B2 as part of STAT545B in the fall of 2021. (more information about the assignment for making an R package and instructions for putting the package together may be found here: [link](https://stat545.stat.ubc.ca/assignments/assignment-b2/))

The goal of `B2package` is to provide a package that contains a function, `data_snapshot()`, that helps to provide a quick and useful snapshot of one's numeric data. Specifically, the function in this package provides a data snapshot of two numeric variables, by returning summary statistics for the numeric variables (mean, median, min and max), as well as a visualization (scatterplot) and the adjusted R squared value to provide a sense of the linear relationship between the variables (if any). Generally, the adjusted r squared value, a value between 0 and 1 (returned as a percentage by the function), represents the proportion of variance observed for a dependent variable explained by the independent variable in a linear regression model. The `data_snapshot()` function therefore allows users of the `B2package` to quickly get a sense of the relationship between two numeric variables in a given dataset (for example, data from a tibble).

## Installation

B2package is not yet on CRAN. But, you can download it from this repository using
the following R command:

``` r
devtools::install_github("hansudd/AssnB2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hansudd/AssnB2", ref = "0.1.0")
```
## Examples (usage demonstration)


__Example 1:__ This is an example that shows you how to quickly visualize and assess the relationship between two numeric variables:
```{r example}
# loading the B2package package
library(B2package)

# we will use two numeric variables from the mtcars dataset, a well known dataset that comes with CRAN

## example 1 of the data_snapshot function 
data_snapshot(mtcars, hp, mpg)



```

Example 1 shows how we can use `data_snapshot()` to quickly explore the linear relationship between two numeric variables from the `mtcars` dataset, hp vs mpg. We observe an adjusted r-squared value of 58.92 %. We also see that two tibbles with some summary statistics for our numeric variables of interest are returned by the function. Example 2 will feature a usage demonstration where there is a stronger linear relationship between the two variables.

__Example 2:__ This is another example that shows you how to quickly visualize and assess the relationship between two numeric variables:
```{r}

# we will use the mtcars dataset, but this time change the mpg variable to the wt variable

# example 2 of the data_snapshot function
data_snapshot(mtcars, mpg, wt)
```

Example 2 shows the linear relationship between the variables mpg and wt from the `mtcars` dataset. Here, we report a higher adjusted r-squared value of 74.46 %. Our function therefore suggests a stronger linear relationship exists between these two numeric variables, in contrast to the variables used in Example 1.

## Summary

Hence, from these two usage examples, we see that the `data_snapshot` function returns summary statistics (two tibbles containing the min, max, mean and median for each numeric variable), a scatterplot and the adjusted r squared value when fed two numeric variables.

This package is helpful if you frequently work on datasets with two numeric variables, and you want to quickly determine if 
there is a linear relationship between the variables. 
